The problem and promise of scale in multilayer animal social networks

### 2020-02-10 paper/manuscript.Rmd
concl
lc is 30 in manuscript

## Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at <!-- TODO:
double check lc res--> 10 m resolution. We reclassified the landcover types into
three categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broadleaf forest, and mixed-wood forest habitat types. Water habitat was
excluded from all subsequent analyses.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology. We
aggregated the 10 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 10 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).

@@

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
--> 
<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Connective redundancy decreased
with increasing landcover resolution due the decrease in connectivity of
individuals in winter forage habitats, resulting in a multilayer network where
neighbours were less frequently repeated in multiple layers <!-- TODO: I'm
having a hard time understanding this previous sentence -->
(Figure\@ref(fig:lcres)d). Layer similarity was generally stable for forest and
open habitats except for a contrasting increase in similarity for forest and
decrease in similarity for open habitats at 250 m landcover resolution (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 10 m
there were no individuals connected in the network layers. <!-- individuals
still used forage but in much lower proportion + lowered opportunity to
associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.
<!-- TODO: how? This isn't clear enough for me to follow yet -->

@@

<!-- Figure 4: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks were constructed for each landcover
class (forest, forage, and open) across two seasons (summer and winter), and four
network metrics were calculated and we examined how network metrics changed as a
function of changes in spatial scale. A) Mean graph strength of individuals was
weaker during the summer compared to the winter months. B) Mean layer relevance
showed sparse connectivity in summer compared to winter networks and a decrease
in winter forage layer relevance at higher landcover resolutions. C) Similarity
of landcover network layers between seasons (e.g. open summer compared to open
winter) showed different responses to changing landcover scale with an increase
in similarity for forest layers at 250 m and decrease in similarity for open
layers at 250 m. Note that forage layer similarity is not shown because
individuals did not interact in forage habitats greater greater than 10 m
landcover resolution. D) Mean connective redundancy across individuals showed a
decreasing trend with increasing landcover resolution.

@@

>>>>

## Landscape data and habitat classification
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at <!-- TODO:
double check lc res--> 30 m resolution. We reclassified the landcover types into
three categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broadleaf forest, and mixed-wood forest habitat types. Water habitat was
excluded from all subsequent analyses.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology. We
aggregated the 30 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation
occurred using a modal moving window method using a circular window
corresponding to the above scales [@Graham_2019a]. We assume 30 m and 100 m
represents fine-scale decision making for caribou during foraging, while
re-sampling at 500 m and 1000 m represents the scale at which caribou tend to
select and avoid habitat (Bastille-Rousseau et al. 2017).

@@

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
--> 
<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Connective redundancy decreased
with increasing landcover resolution due the decrease in connectivity of
individuals in winter forage habitats, resulting in a multilayer network where
neighbours were less frequently repeated in multiple layers <!-- TODO: I'm
having a hard time understanding this previous sentence -->
(Figure\@ref(fig:lcres)d). Layer similarity was generally stable for forest and
open habitats except for a contrasting increase in similarity for forest and
decrease in similarity for open habitats at 250 m landcover resolution (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 30 m
there were no individuals connected in the network layers. <!-- individuals
still used forage but in much lower proportion + lowered opportunity to
associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.
<!-- TODO: how? This isn't clear enough for me to follow yet -->

@@

<!-- Figure 4: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks were constructed for each landcover
class (forest, forage, and open) across two seasons (summer and winter), and four
network metrics were calculated and we examined how network metrics changed as a
function of changes in spatial scale. A) Mean graph strength of individuals was
weaker during the summer compared to the winter months. B) Mean layer relevance
showed sparse connectivity in summer compared to winter networks and a decrease
in winter forage layer relevance at higher landcover resolutions. C) Similarity
of landcover network layers between seasons (e.g. open summer compared to open
winter) showed different responses to changing landcover scale with an increase
in similarity for forest layers at 250 m and decrease in similarity for open
layers at 250 m. Note that forage layer similarity is not shown because
individuals did not interact in forage habitats greater greater than 30 m
landcover resolution. D) Mean connective redundancy across individuals showed a
decreasing trend with increasing landcover resolution.

@@

In summary, blah blah
